\section*{Experience}
	{\gtsectramedium\color{GriffinGreyBold} Mathematics Researcher}, {\gtsectrabook Northeastern University} \hfill Fall 2024 -- Present
	\cbox{\begin{itemize}
			\item Developing classification theory for chiral polytopes with automorphism groups of order $2^k p$, collaborating with advisor Egon Schulte on intractable enumeration problem requiring novel approaches.
			\item Introduced concept of ``basal polytopes'' as minimal building blocks; this framework accounts for the majority of chiral polyhedra of order $2^k p \leq 2000$.
			\item Presented research at WIMIN conference at Smith College, and seminars for NSMRP and GSS.
			\item Co-authoring paper ``Chiral polyhedra from $\mathrm{AGL}(1,q)$'' with E. Schulte on novel classification methods stemming from basal framework.
		\end{itemize}}
	\smallskip

	{\gtsectramedium\color{GriffinGreyBold} Directed Reading Program (DRP) Mentor \& Committee Member}, {\gtsectrabook Northeastern University} \hfill Jan. 2023 -- Present
	\cbox{\begin{itemize}
			\item Mentored 10+ advanced undergraduates in discrete math, topology, diff. geom., and combinatorics.
			\item Maintained typeset collection of notes in \LaTeX{} for each group as term progressed, complete with their observations and conjectures to be proven by term's end.
			\item Intentionally structured meetings around having students discover theorems in explorations before encountering them in readings.
		\end{itemize}}
	\smallskip

	{\gtsectramedium\color{GriffinGreyBold} Instructor of Record \& Teaching Assistant}, {\gtsectrabook Northeastern University} \hfill Sept. 2022 -- Present
	\cbox{\begin{itemize}
			\item Instructor of Record for MATH1365 Introduction to Mathematical Reasoning; designed lectures, wrote comprehensive course notes, and ran \LaTeX{} workshops to support clear mathematical writing.
			\item Led conference-style classroom: posed carefully designed questions to prompt student discovery of concepts before formal presentation, positioning instructor as facilitator of student ideas.
			\item Began classes with story relevant to material to make mathematics verbal, spoken, and argumentative rather than purely computational.
			\item Maintained extensive availability through numerous office hours, review sessions, and active communication to encourage genuine engagement with mathematics.
			\item Achieved above-university-mean student evaluations; two students from instructor-of-record course specifically sought continued mentorship through DRP.
			\item Taught a variety of courses ranging from 8 to 50+ students with consistent enthusiasm; emphasized working strictly from definitions to build proof-writing skills and effective problem-solving.
		\end{itemize}}
	\smallskip

	{\gtsectramedium\color{GriffinGreyBold} Northeastern Summer Math Research Program (NSMRP) Mentor}, {\gtsectrabook Northeastern University} \hfill May 2025 -- Sept. 2025
	\cbox{\begin{itemize}
			\item Co-mentored 6 undergraduates in NSF-funded REU on graph theory, combinatorics, and pursuit-evasion games; led daily meetings, facilitated discussions in Discord.
			\item Published 2 papers as a result of combined efforts by researchers and mentors.
		\end{itemize}}
	\smallskip

	{\gtsectramedium\color{GriffinGreyBold} Mathematics Researcher}, {\gtsectrabook Reed College} \hfill Spring 2020 -- Fall 2021
	\cbox{\begin{itemize}
			\item Investigated Ehrhart polynomials of cyclic polytopes and extensions to general Euler-Maclaurin formulas using methods of advisor Jamie Pommersheim.
			\item Developed recursive decomposition of normal cones to vertices of cyclic polytopes; wrote and defended year-long senior thesis ``Cyclic cones \& non-singular refinements of cyclic normal fans.''
		\end{itemize}}